\section{Referencias}

\begin{itemize}
    \item Brown, R. W., Cheng, Y.-C. N., Haacke, E. M., Thompson, M. R., \& Venkatesan, R. (2014). 
    \textit{Magnetic Resonance Imaging: Physical and Biological Principles} (4ª ed.). Wiley.

    \item Dawson, M. J. (2013). 
    \textit{Paul Lauterbur and the Invention of MRI}. MIT Press.

    \item Lauterbur, P. C. (1973). 
    Image formation by induced local interactions: Examples employing nuclear magnetic resonance. 
    \textit{Nature, 242}(5394), 190–191.

    \item Mansfield, P. (1977). 
    Multi-planar image formation using NMR spin echoes. 
    \textit{Journal of Physics C: Solid State Physics, 10}(3), L55–L58.

    \item Slichter, C. P. (1990). 
    \textit{Principles of Magnetic Resonance} (3ª ed.). Springer.

    \item Semelka, R. C. (Ed.). (2015). 
    \textit{MRI: Basic Principles and Applications}. Wiley.

    \item Nobel Prize Committee. (2003). 
    The Nobel Prize in Physiology or Medicine 2003: Paul C. Lauterbur and Sir Peter Mansfield. 
    \textit{NobelPrize.org}. Recuperado de \url{https://www.nobelprize.org/prizes/medicine/2003/summary/}

    \item National Center for Biotechnology Information. (2018). 
    Magnetic Resonance Imaging: The Nuclear Option. 
    \textit{PubMed Central}. Recuperado de \url{https://pmc.ncbi.nlm.nih.gov/articles/PMC5988242/}

    \item Huettel, S. A., Song, A. W., \& McCarthy, G. (2015). 
    \textit{Introduction to Functional Magnetic Resonance Imaging: Principles and Techniques} (2ª ed.). Cambridge University Press.

    \item Scott, A. D., et al. (2006). 
    Magnetic Resonance Imaging: Historical Perspective. 
    \textit{Journal of Cardiovascular Magnetic Resonance, 8}(4), 573–580. 
\end{itemize}